\chapter{Introduction}

\textit{``... Pleasure has probably been the main goal all along. But I hesitate to admit it, because computer scientists want to maintain their image as hard-working individuals who deserve high salaries. Sooner or later society will realize that certain kinds of hard work are in fact admirable even though they are more fun than just about anything else. (Knuth 1993)''} \cite{oneliners}

Computers are being used for amazing things. There are computers that can verify faces with sight, computers that can determine music by hearing it, and computers that react to touch. But, with all of these advancements, programmers have yet to provide computers with the most important, essential, and human sense: a sense of humor. This is a sense so complicated that, while we have hearing aids and glasses, nothing fixes a terrible sense of humor. But maybe modern technology can help.

Much work has been done in the field of computational humor, both in trying to understand and generate humor. Although there has been success in humor identification, it has always been directed at understanding specific kinds of jokes. For example, understanding if a sentence can be made into a ``That's What She Said'' joke\cite{twss} is great, but their technique only works for that specific kind of joke. One liner identification \cite{oneliners} and pun generators, although great achievements in the field of computational humor, still suffer from being about a specific form of joke, and thus are hard to apply outside of their scope.

This work attempts to widen the scope of humor recognition beyond narrow joke structures by attempting to predict laughter in TED talks.

\section{Laugh Prediction}
Laugh prediction is the ability to, after a line is said, predict how likely it is that it will be followed by a laugh. In a sense, this is trying to identify whether something was a punchline of a funny joke, without needing to discover what the joke is or why it is funny. We believe this can be done by analyzing paragraph structure and word choice, as well as humorous stylistics.

\section{Applications of Laugh Prediction}
Laughter is an essential part of being human, and humor has been ingrained into our species no matter the culture. On a grand scale, an AI that is able to laugh at a correct time would be a major step towards creating a more human like AI. However, let's look at more immediate uses for laugh prediction as well.

When it comes to researching humor, laugh prediction will allow new perspectives on joke structure and design. This can provide new insight on the joke telling process. With some fine tuning, a user might be able to practice their delivery style on specific environments; such as wedding ceremonies or political speeches. 

Laugh prediction could be used to test if something will merit a laugh in fields like advertising. This is important, as the repercussions from poorly made jokes can be massive when it comes to major advertisements. However, this risk comes with high reward, as humorous commercials tend to be memorable.

Lastly, laugh prediction will be able to improve human computer interaction when it comes to vocal communication. It will make the computer appear more human, as it will appear to have a sense of humor. Adding humor into human computer interaction has been proven to improve people's opinions of it.\cite{Teaching}\cite{Multi-Humoroid} Imagine a world where you can tell Siri or Cortana a joke, and it would be able to laugh (or groan) accordingly. 

\section{Application}
This work outlines an application that attempts to predict when there will be laughter in a text script. The application uses machine learning and natural language processing (NLP) to analyze the script, and make predictions after each line based off of the training scripts. We trained our application using transcripts from TED Talks. The application was successfully able to predict laughter. We believe that with a different training corpus, this application can be used with other environments such as political speeches.

\subsection{Why TED Talks? Does It Matter?}
I would like you to think up something you once heard that was really funny and made you laugh loudly. A literal ``LOL'' moment, if you will. I'll give you 5 minutes.

Got it? Good. Now imagine you were at a bar, drinking whatever you choose, surrounded by your friends who are having a great time. Do you think your funny moment would get them to laugh? Most likely yes, as that atmosphere can make most things funny. Now try this again but at a sad funeral. Chances are that you wouldn't get a laugh at such a solemn event. Humor is as much about the environment as it is about what is said and done. Because of this, we had to pick an environment to train our system on. We chose TED Talks because TED Talk transcripts were the only ones we found where laughter is recorded. 

\section{Contribution}
The goal of this project was to show that it is possible for a computer system to be able to predict laughter without needing depending on a narrow joke structure such as knock knock joke or pun. Although the project was a success, more research needs to be done to generalize this beyond TED Talks. 

This project has also contributed to the field of NLP as a whole by creating a corpus of TED Talks, free to use by anyone.
